### 2023-11-07 Data/AnalysisData/codebook_Plot_46_data.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:59:14.419679"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_Plot_26_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:47.216976"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_Plot_46_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H3_avg.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:47.475669"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H4_avg.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:55.749084"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H3_avg.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H3_multiple.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:41.005817"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H4_multiple.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:53.662957"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_data_H3_multiple.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_data_H4.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:53.662957"
output: github_document
---

@@

## Dataset description
The data contains 713 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H3_multiple.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:23.774949"
output: github_document
---

@@

## Dataset description
The data contains 154 cases and 90 variables.

@@

```{r}
summaries <- read.csv("codebook_data_H4.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_plot_23_data_alpha.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:03:49.637916"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_34_data_alpha.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:58.540839"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_23_data_alpha.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_plot_23_data_omega.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:04:46.430554"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_34_data_omega.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:59:02.156609"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_23_data_omega.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Data/AnalysisData/codebook_plot_456_data.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 10:58:51.91642"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_256_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:44.141596"
output: github_document
---

@@

```{r}
summaries <- read.csv("codebook_plot_456_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2023-11-07 Scripts/Manuscript/manuscript.Rmd
changed the naming for the hypothesis related functions to match the hypothesis numbering in the manuscript.

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```
The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability. The formula used to calculate the ICC is presented below.

@@

@@

@@

>>>>

```{r Final Preparation of Data}
### this code prepares the various pieces of data to be ready to use for the analyses.
## confirmatory analyses
# for hypothesis 4
data_H4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_H5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_H6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

# for hypothesis 1
data_H1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
# for hypothesis 2
data_H2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, 
  data_1.12.3.2_clean, data_2.10.1_clean, data_2.12.1_clean, data_2.12.2_clean, 
  data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, 
  data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.2_clean, data_3.8.2_clean, 
  data_5.1.1_clean, data_5.7_clean, data_5.9.1_clean)
# for hypothesis 3
data_H3_multiple <- Data_prep_H3_multiple(data_H5, data_H2)
data_H3_avg <- Data_prep_H3_avg(data_H5, data_H3_multiple)

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_H6)
# plot accompanying the results for Hypotheses 4, & 6
Plot_46_data <- data_prep_plot_46(data_H6[c(3, 6, 9, 12, 15, 36, 39, 42, 45, 48)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_H3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_H3_multiple)

### Exporting the final datasets for the analyses
# the open data
open_data(data = data_H4, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H4))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H4))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H4))), ".yml"))

open_data(data = data_H6, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H6))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H6))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H6))), ".yml"))

open_data(data = data_H5, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H5))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H5))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H5))), ".yml"))

open_data(data = data_H1, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H1))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H1))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H1))), ".yml"))

open_data(data = plot_456_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_456_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_456_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_456_data))), ".yml"))

open_data(data = Plot_46_data, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(Plot_46_data))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(Plot_46_data))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(Plot_46_data))), ".yml"))

open_data(data = data_H2, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H2))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H2))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H2))), ".yml"))

open_data(data = data_H3_multiple, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H3_multiple))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H3_multiple))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H3_multiple))), ".yml"))

open_data(data = data_H3_avg, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_H3_avg))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_H3_avg))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_H3_avg))), ".yml"))

open_data(data = plot_23_data_alpha, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_23_data_alpha))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_23_data_alpha))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_23_data_alpha))), ".yml"))

open_data(data = plot_23_data_omega, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_23_data_omega))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_23_data_omega))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_23_data_omega))), ".yml"))

# clearing up memory space by removing intermediate files from the environment
rm(coded_data_original, coded_data_original_shortened, coded_data_replications)

@@

```{=tex}
\begin{align*}
& Level 1: alpha_{ij} = \beta_{0j} + e_{ij} \qquad\qquad\quad e_{ij} \sim N(0, \sigma_{e}^{2}) \\
& Level 2: \beta_{0j} = \gamma_{00} + u_{0j} \qquad\qquad\qquad u_{0j} \sim N(0, \sigma_{u0}^{2}) \\
& Mixed: alpha_{ij} = \gamma_{00} + u_{0j} + e_{ij}
\end{align*}
```

```{r Hypothesis 2 Model}
# intercept only model to check the within and between group variance.
H2_test_result_alpha <- summary(lmer(formula = alpha ~ 1 + (1|g), data = data_H2))

# and same analyses for omega
# intercept only model to check the within and between group variance.
H2_test_result_omega <- summary(lmer(formula = omega.tot ~ 1 + (1|g), data = data_H2[complete.cases(data_H2),]))

The purpose of this analysis was to investigate variability in calculated reliability coefficients within and between replication sets. However, to the author's knowledge no formal test exists as of the writing of this thesis for testing the significance of within group variance after controlling for between group variance. Instead the intraclass correlation (ICC) coefficient was calculated an indicator of within vs. between variability. The formula used to calculate the ICC is presented below.

@@

```{r ICC calculations}
# alpha
# within group variance: 0.04384
# between group variance: 0.19824
ICC_alpha <- 0.19824 / (0.04384 + 0.19824)

# omega
# within group variance: 0.003779
# between group variance: 0.034025
ICC_omega <- 0.034025 / (0.003779 + 0.034025)

@@

```{r Hypothesis 3 Main Test}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_result_main_alpha <- summary(glm(formula = replication ~ 1 + alpha_avg, 
                                     family = binomial(), data = data_H3_avg))

# and for omega
H3_test_result_main_omega <- summary(glm(formula = replication ~ 1 + 
                                     omega.tot_avg, family = binomial(), 
                                     data = data_H3_avg))

# alpha says negative, omega says positive, neither are significant though.

@@

```{r Hypothesis 3 Multilevel Model Sensitivity Analyses}
## sensitivity analyses.
# running a random intercept multilevel logistic model
H3_test_result_int_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1|g), family = 
                                                binomial(), data = 
                                                data_H3_multiple))

# and for omega
H3_test_result_int_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1|g), family = 
                                                  binomial(), data = 
                                                  data_H3_multiple))

# same as for non-multilevel model

# running a random slope multilevel logistic model
H3_test_result_slp_sensitivity_alpha <- summary(glmer(formula = replication ~ 1 
                                                + alpha + (1 + alpha|g), 
                                                family = binomial(), data =
                                                data_H3_multiple))

# and for omega
H3_test_result_slp_sensitivity_omega <- summary(glmer(formula = replication ~ 1 
                                                + omega.tot + (1 + omega.tot|g), 
                                                family = binomial(), data =
                                                data_H3_multiple))

# alpha did not converge, and omega shows no significant effect.
```
